The Hosting Environment of the Advanced Resource Connector middleware

### 2008-08-31 doc/hed/ARCHED_article.tex
One more update of HED document

%-------- Change this to NORDUGRID-XXXXXXX-NN

{\raggedleft NORDUGRID-XXXXXXX-NN\par}

@@

This document does not (yet?) include in depth description of C++ classes which constitute the HED. Instead most section contain notes entitled "Relevant classes". Technical description of those classes can be found in automatically generated "Hosting Environment (Daemon) Reference Manual" document [].

For examples please see source code in repository []. Many components and libraries are accompanied with test and example applications.

@@

Each MCC has an entry method \texttt{process} which is called with Message being processed. It then processes Message by modifying it or creating new Message. Then MCC calls entry method of next MCC in the chain. For information how messages are handled and about memory management policies please see API description of MCC class in [].

@@

Here only basic information about security related objects is presented. For more detailed information please see "Security Framework of ARC1" [].

@@

The value if Secuirity Attribute is an object of class inherited from SecAttr. The HED implements class SecAttr which serves as definition of interface for all Security Attributes. It defines way collected information may be turned into useful format. For that each Security Attribute value implements method Export for converting internal information into one of supported formats. Currently only implemented is ARC Authorization Request/Policy (see below). Please see API description of SecAttr and MessageAuth classes in [] for more information.

@@

@@

\texttt{Relevant classes: Arc::DataPoint, Arc::DataMover and related classes.}

@@

Along with ordinary endpoints defining location of data directly - like HTTP, FTP, LDAP - the DMC can be used with indirect/indexing endpoints. Those are endpoints which define only location of meta-data associated with actual data or an interface/service providing functionality of managing/requesting data.

% TODO a lot

@@

@@

>>>>

{\raggedleft NORDUGRID-TECH-19\par}

@@

This document does not (yet?) include in depth description of C++ classes which constitute the HED. Instead most section contain notes entitled "Relevant classes". Technical description of those classes can be found in automatically generated "Hosting Environment (Daemon) Reference Manual" document \cite{hed-api}.

For examples please see source code in repository \cite{svn-arc1}. Many components and libraries are accompanied with test and example applications.

@@

Each MCC has an entry method \texttt{process} which is called with Message being processed. It then processes Message by modifying it or creating new Message. Then MCC calls entry method of next MCC in the chain. For information how messages are handled and about memory management policies please see API description of MCC class in \cite{hed-api}.

@@

\texttt{Relevant classes: Arc::SecAttr}

Here only basic information about security related objects is presented. For more detailed information please see "Security Framework of ARC1" \cite{sec-arc1}.

@@

The value if Secuirity Attribute is an object of class inherited from SecAttr. The HED implements class SecAttr which serves as definition of interface for all Security Attributes. It defines way collected information may be turned into useful format. For that each Security Attribute value implements method Export for converting internal information into one of supported formats. Currently only implemented is ARC Authorization Request/Policy (see below). Please see API description of SecAttr and MessageAuth classes in \cite{hed-api} for more information.

@@

\texttt{Relevant classes: ArcSec::SecHander}

@@

\texttt{Relevant classes: Arc::DataPoint, Arc::DataMover, Arc::DataBuffer and related classes.}

@@

Along with ordinary endpoints defining location of data directly - like HTTP, FTP, LDAP - the DMC can be used with indirect/indexing endpoints. Those are endpoints which define only location of meta-data associated with actual data or an interface/service providing functionality of managing/requesting data. For more information about indexing endpoints see description of supported URLs in \cite{urls}.

More in depth techical information about the DMC can be found in \cite{dmc}.

@@

The server and client side MCCs are called \texttt{tcp.service} and \texttt{tcp.client} correspondingly. They are located in the shared library called \texttt{mcctcp}.

@@

\bibliography{grid}
